Supplementary materials: Reproducibility of SNV-calling in multiple sequencing runs from single tumors

### 2015-10-23 PAPER/Supplementary.tex
finished supplementary

>>>>

\begin{figure}
\centerline{
\includegraphics[width=5in]{QualFigure1.pdf} }
\caption{\textbf{Number of putative SNVs in a sample does not correlate with coverage.} The number of SNVs called in a sample does not correlate with the coverage of that sample  (Spearman $\rho=-0.1255027$, $S=671817.1$, $P=0.1222$).} 
\label{fig:coverage}
\end{figure}

\begin{figure}
\centerline{
\includegraphics[width=5in]{QualFigure2.pdf} }
\caption{\textbf{Number of putative SNVs in a sample does not correlate with percentage of mapped reads.} The number of SNVs called in a sample does not correlate with the percentage of mapped reads in the alignment of that sample  (Spearman $\rho=-0.06771965$, $S=637326.1$, $P=0.4056$).} 
\label{fig:percent_mapped}
\end{figure}
